Single-step Hybrid Predition

### 2016-12-07 reports/transformed_kernels.Rmd
Fix merge conflict

  cmb_lst[] <- lapply(seq_along(cmb_lst), FUN = function(i) {
    nm <- names(cmb_lst)[i]
    dat <- cmb_lst[[nm]]
    dat$geno <- hyb_names_pred_size[[nm]]
    dat
  })
  cmb_lst
})
names(trans_cat_lst) <- pred_sets %>%
  map(~paste(., collapse = "_")) %>%
  flatten_chr()
trans_cat_lst <- trans_cat_lst %>%
  transpose()

>>>>

  cmb_lst[] <- lapply(seq_along(cmb_lst), FUN = function(i) {
    nm <- names(cmb_lst)[i]
    dat <- cmb_lst[[nm]]
    dat$geno <- hyb_names_pred_size[[nm]]
    dat
  })
  cmb_lst
})
names(trans_cat_lst) <- pred_sets %>%
  map(~paste(., collapse = "_")) %>%
  flatten_chr()
trans_cat_lst <- trans_cat_lst %>%
  transpose()
saveRDS(trans_cat_lst, 
        file = "./data/derived/transformed_pred_sub_list.RDS")
